---
title: "HW 02: Analysis of Variance"
author: "Your Name"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE)
```

## Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(broom)
library(knitr) 
```

## Part 1: Computations & Concepts 

### Question 1

```{r anova-values}
dfw <- 125 # degrees of freedom within (residuals)
dft <- 130 # total degress of freedom
ssw <- 6.486 # sum of squares within (residuals)
sst <- 19.386 # total sum of squares
```

(Type the response to Question 1 here.)

### Question 2



### Question 3



### Question 4



### Question 5



## Part 2: Data Analysis

### Question 6

```{r}
stress_data <- read_csv("data/stress-experiment.csv")
```

(Add code and narrative as needed.)

### Overall (Do not delete!)

You do not need to write anything for this question. We will check the following as part of your lab grade: 

- 5 pt: Documents neatly organized (.Rmd and .md files)	
- 3 pt: Narrative in full sentences and neatly organized
- 2 pt: Regular and informative commit messages	


