---
title: "HW 02: Analysis of Variance"
author: "Your Name"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE)
```

## Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(broom)
library(knitr) 
```

## Part 1: Computations & Concepts 

### Question 1

```{r anova-values}
dfw <- 125 # degrees of freedom within (residuals)
dft <- 130 # total degress of freedom
ssw <- 6.486 # sum of squares within (residuals)
sst <- 19.386 # total sum of squares
dfb <- 5 # degrees of freedom between (model)
ssb <- 12.9 # sum of squares between (model)
msb <- 2.58  # mean square between
msw <- 0.0519  # mean square within (residuals)
f_stat <- 49.722  #F -statistic 
p_val <- 1-pf(49.722, 5, 125)  # F-Statistic, DF1, DF2
```

```{r anova-table}
source <- c("Between Groups", "Within Groups", "Total")
df <- c(dfb, dfw,dft)
ss <- c(ssb, ssw, sst)
ms <- c(msb, msw,NA)  
f.statistic <- c(f_stat, NA, NA)
p.value <- c(p_val,NA,NA)

# combine the columns to make a table called "anova"
anova <- bind_cols("Source"=source,"df"=df,"Sum of squares"=ss,"Mean square"=ms,"F-statistic"=f.statistic,"p-value"=p.value)

# print the table 
kable(anova) 
```


### Question 2

131 observations are in the dataset. DF total (130) is n-1, so n=131. 
6 groups are being compared. DF between (5) is K-1, so K=6.

### Question 3

The estimate of σ2 is MSW. The mean square within is 0.0519, and it measures the variance within each group.

### Question 4

The null hypothesis states there is no statistically significant difference between the means in across the 6 groups. The alternative hypothesis states there is at least one mean in the 6 groups that is not equal to the others.

H0:μ1=μ2=μ3=μ4=μ5=μ6

Ha:At least one μ is not equal to the others

### Question 5

The p-value of 0 is less than the alpha level 0.05, therefore we reject the null hypothesis, in favor of the alternative hypothesis. There is at least one mean in the 6 groups that is not equal to the others.

## Part 2: Data Analysis

### Question 6

```{r}
stress_data <- read_csv("data/stress-experiment.csv")
```

(Add code and narrative as needed.)

### Overall (Do not delete!)

You do not need to write anything for this question. We will check the following as part of your lab grade: 

- 5 pt: Documents neatly organized (.Rmd and .md files)	
- 3 pt: Narrative in full sentences and neatly organized
- 2 pt: Regular and informative commit messages	


