---
title: "HW 02: Analysis of Variance"
author: "Your Name"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning=FALSE, 
                      message=FALSE)
```

## Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(broom)
library(knitr) 
```

## Part 1: Computations & Concepts 

### Question 1

```{r anova-values}
dfw <- 125 # degrees of freedom within (residuals)
dft <- 130 # total degrees of freedom
ssw <- 6.486 # sum of squares within (residuals)
sst <- 19.386 # total sum of squares
dfb <- 5 # degrees of freedom between (model)
ssb <- 12.9 # sum of squares between (model)
msb <- 2.58  # mean square between
msw <- 0.0519  # mean square within (residuals)
f_stat <- 49.722  #F -statistic 
p_val <- 1-pf(49.722, 5, 125)  # F-Statistic, DF1, DF2
```

```{r anova-table}
source <- c("Between Groups", "Within Groups", "Total")
df <- c(dfb, dfw,dft)
ss <- c(ssb, ssw, sst)
ms <- c(msb, msw,NA)  
f.statistic <- c(f_stat, NA, NA)
p.value <- c(p_val,NA,NA)

# combine the columns to make a table called "anova"
anova <- bind_cols("Source"=source,"df"=df,"Sum of squares"=ss,"Mean square"=ms,"F-statistic"=f.statistic,"p-value"=p.value)

# print the table 
kable(anova) 
```


### Question 2

There are 131 observations are in the dataset. DF total (130) is n-1, so n=131. 

There are 6 groups being compared. DF between (5) is K-1, so K=6.

### Question 3

The estimate of σ2 is the mean square within (MSW). The MSW is 0.0519, and it measures the variance within each group.

### Question 4

The null hypothesis states there is no statistically significant difference between the means in across the 6 groups. The alternative hypothesis states there is at least one mean in the 6 groups that is statistically significantly different from the others.

H0: μ1=μ2=μ3=μ4=μ5=μ6

Ha: At least one μ is not equal to the others

### Question 5

The p-value of 0 is less than the alpha level 0.05, therefore we reject the null hypothesis, in favor of the alternative hypothesis. There is at least one mean in the 6 groups that is not equal to the others.

## Part 2: Data Analysis

### Question 6

```{r}
stress_data <- read_csv("data/stress-experiment.csv")
```

#### Exploratory Data Analysis

Create side-by-side boxplots to visualize distribution of heart rate by group (control, friend present, pet present).

``` {r boxplot}
ggplot(data = stress_data, mapping = aes(y = heart_rate, x = group)) + geom_boxplot() + labs(title = "Distribution of Heart Rate by Group", x = "Group", y = "Heart Rate")
```

Create density plot to show distribution of heart rate by group.

```{r density-plot}
ggplot(data = stress_data, aes(x = heart_rate, fill = group)) +
  geom_density(alpha = 0.5) + 
  labs(title = "Heart Rate Distribution by Group", 
       x = "Heart Rate", 
       color = "Group")
```

Summarize mean and variance for each group.

```{r summary}
stress_data %>%
  group_by(group) %>%
  summarise(mean = mean(heart_rate), variance=var(heart_rate))
```

#### Assumptions

Normality is not satisfied because the density plot distributions are not normal for any group. The 'control' and 'friend present' group distributions are skewed left, and the 'pet present' group distribution is skewed right.

Equal (Constant) Variance is satisfied because we see that none of the groups' variances are more than four times the other variances.

Independence is satisfied because one woman's heart rate/stress response does not affect another's. The observations are independent subjects who have no influence on each other.

#### Hypotheses

The null hypothesis is there is no statistically significant difference in mean heart rate between the groups of women. The alternative hypothesis is there is at least one mean heart rate that is statistically significantly different thatn the others.

H0: μ1=μ2=μ3

Ha: At least one μ is not equal to the others

#### ANOVA Test

```{r anova}
heartrate_anova <- aov(heart_rate ~ group, data = stress_data)
tidy(heartrate_anova) %>% kable(format = "markdown", digits = 5)
```

The p-value of 0.00002 is less than the alpha level 0.05, so we reject the null hypothesis, in favor of the alternative hypothesis. Thus, there is at least one mean heart rate that is statistically significantly different than the others.

The estimate of σ2 is the mean square within (MSW). The MSW is 84.793, and it measures the variance within each group.

```{r intervals}
n.groups <- stress_data %>%
  distinct(group) %>% 
  count()

crit.val <- qt(0.975, (nrow(stress_data)-n.groups$n))
sigma <- sqrt(84.79285)

conf.intervals <- stress_data %>%
  group_by(group) %>% 
  summarise(mean = mean(heart_rate), n = n(), 
            lower = mean - crit.val * sigma/sqrt(n),
            upper = mean + crit.val * sigma/sqrt(n))
ggplot(data=conf.intervals,aes(x=group,y=mean)) +
  geom_point() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.1) + 
  labs(title="95% Confidence Interval for the Mean Value of Heart Rate", x = "Heart Rate", y = "Group", subtitle="by Group") +
  coord_flip()
```

```{r pairwise}
library(pairwiseCI)
pairwiseCI(heart_rate ~ group, data = stress_data, method = "Param.diff", conf.level = 0.995, var.equal = TRUE)
```

### Overall (Do not delete!)

You do not need to write anything for this question. We will check the following as part of your lab grade: 

- 5 pt: Documents neatly organized (.Rmd and .md files)	
- 3 pt: Narrative in full sentences and neatly organized
- 2 pt: Regular and informative commit messages	


